\vspace{-2cm} Content of Municipal Government Websites

### 2017-03-01 paper/manuscript.tex
added top term frequencies

>>>>

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Mar  1 11:55:24 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{rr}
		\hline
		& tf \\ 
		\hline
		tax & 176324 \\ 
		date & 98949 \\ 
		due & 97192 \\ 
		amt & 96382 \\ 
		town & 86726 \\ 
		value & 81119 \\ 
		total & 70825 \\ 
		parcel & 63589 \\ 
		county & 56201 \\ 
		market & 51758 \\ 
		east & 51357 \\ 
		full & 51199 \\ 
		nrth & 50566 \\ 
		book & 50306 \\ 
		deed & 50231 \\ 
		bill & 49719 \\ 
		acres & 48935 \\ 
		acct & 44871 \\ 
		csd & 43792 \\ 
		owners & 43510 \\ 
		res & 41803 \\ 
		family & 36883 \\ 
		fire & 35156 \\ 
		school & 33685 \\ 
		name & 30382 \\ 
		red & 30362 \\ 
		taxable & 30248 \\ 
		hook & 29902 \\ 
		homestead & 29287 \\ 
		outside & 28593 \\ 
		\hline
	\end{tabular}
	\caption{Top term frequencies for 10 test websites} 
\end{table}
